{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-30 bmvc_review.tex
Comments Replied

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter is a well, known single target
tracking method and the theory and its work flow has been detailed in
other papers already
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the fact that the correlation
filter framework represents training examples as the circulant matrix
and the circulant matrix can be represented as a diagonal matrix by
the discrete Fourier transform.

@@

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To evaluate the performance of the proposed algorithm, we choose two
public, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We
aims at developing an object tracking algorithm that ``efficiently''
runs on an embedded system in ``high speed,'' $\ge 300$ fps, e.g.,
running our tracking algorithms on a drone. Given this, we believe
that the UAV123 video data is a better fit in evaluating the
performance of the proposed algorithm than any other existing tracking
datasets. This is because there are many challenging scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is important to compare the performance of the
proposed algorithm with those of the state-of-the-art in nominal
dataset for comparison. To this end, we chose the OTB100 data that
contains the videos recorded from smart phones and typical cameras in
perspective view. Finally, the {\it E}nKCF2 is tested on temporally
down-sampled version of the UAV123 dataset, we call
``UAV123$\_$10fps'' dataset.

@@

>>>>

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter is a well, known single target
tracking method and the theory and its work flow has been detailed in
other papers already \cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the correlation
filter framework representing training examples as a circulant matrix. To reduce complexity, the
circulant matrix can be diagonalized by Discrete Fourier Transform.  This way, off-diagonal elements become
zero whereas the diagonal elements represent the eigenvalues of the circulant matrix. The egienvalues are equal
to the DFT transformation of the base sample ($x$) elements. The Kernelized Correlation Filter, on the other hand,
applies a kernel to $x$ to transform to a more discriminative domain. The circulant matrix is then formed by applying
cylic shifts on the kernelized $x$. Such kernelization operation does not introduce additional complexity to the baseline
correlation filter framework.

@@

{\it YoungWoo : I edited it based on your comment}

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To evaluate the performance of the proposed algorithm, we choose two
public, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We
aims at developing an object tracking algorithm that ``efficiently''
runs on an embedded system in ``high speed,'' $\ge 300$ fps, e.g.,
running our tracking algorithms on a drone. Given this, we believe
that the UAV123 video data is a better fit in evaluating the
performance of the proposed algorithm than any other existing tracking
datasets. This is because there are many challenging scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is important to compare the performance of the
proposed algorithm with those of the state-of-the-art in nominal
dataset for comparison. To this end, we chose the OTB100 data that
contains the videos recorded from smart phones and typical cameras in
perspective view. Finally, the {\it E}nKCF2 is tested on temporally
down-sampled version of the UAV123 dataset, called UAV123$\_$10fps dataset. 
This way, by modifying the proposed {\it E}nKCF framework slightly we can tackle scenarios dominated by extreme camera and object
motion as we run multiple correlation filter at each frame. One can also perform such modifications based on the hardware specifications. 
A more sophisticated hardware can be more friendly to apply multiple correlation filter ({\it E}nKCF2) at one frame
whereas the ones on the low end can only accommodate a single correlation filter at each frame ({\it E}nKCF).

@@

{\it YoungWoo: I edited the preceding paragraph based on your comment.}
